\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-07-10 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	modified:   reference/sort_values.txt

% Police brutality, law enforcement, and crime: Evidence from Chicago
\begin{abstract}
    \noindent This study examines the impact of offline store expansion by Lianjia, China's leading real estate brokerage, within the framework of platform-mediated consolidation. By analyzing micro-level transactions of second-hand houses from Lianjia in ten major Chinese cities from 2016 to 2022, this research investigates how the transaction patterns of traditional brokerages, characterized by the strategic clustering of offline stores, transition towards platform-mediated consolidation, thereby facilitating the development of an extensive franchise network. Utilizing a regression discontinuity design (RDD), the study quantifies the optimal influence radius of offline stores (410 meters) on housing transactions. Incorporating this optimal influence radius, the study further empirically estimates the effects of real estate brokerage's offline store expansion and platform-based consolidation on transaction properties. The results indicate that this strategy significantly boosts revenues and attracts more people to housing tours. The results also suggest that neither the platform-based strategy nor offline expansion affects the transaction period, but offline store expansion can indeed reduce the price gap between sellers and buyers. Additionally, we proposed a measure of the network effect and found that Lianjia's offline stores show a local clustering pattern with moderate network strength. We then analyzed the effect of platform-mediated consolidation on network strength and concluded that the effect is significantly positive. This study provides valuable insights into the synergy between offline store expansion and online platform development, elucidating future trajectories in the evolving real estate brokerage market and analogous sectors.
  \end{abstract}

@@

Understanding housing markets is crucial due to their significant impact on household finance, as housing is typically the largest component of a household's portfolio. The illiquidity of housing creates a strong link between housing and labor markets, and transaction costs are critical for buyers and sellers in the real estate market. Real estate brokers play a vital role in reducing these costs, providing essential market information, negotiation support, and legal assistance to ensure smoother and more efficient transactions. With the improvement of China's legal system in the real estate market, the brokerage market is expanding and becoming more prosperous. Especially in the context of China's burgeoning real estate market, brokerage firms are assuming an increasingly important role in facilitating the communications between buyers and sellers \citep{glaeser_real_2017}. Given the heterogeneous and "thin" nature of real estate goods \citep{HAN2015813}, the expertise and local market knowledge of real estate brokers have become indispensable in navigating the complex real estate landscape.

China's real estate listings market possesses distinct features characterized by the prominence of offline stores, setting it apart from the markets in other developed countries. Compared to the United States, where the Multiple Listing Service (MLS) provides comprehensive and reliable information online, facilitating transactions in a market where houses are typically situated far apart, the role of offline real estate stores is minimized. In contrast, China's real estate market is predominantly offline-based, with online listings serving mainly as references. Face-to-face interactions remain crucial for transactions. Additionally, the Chinese government imposes stringent restrictions on the online listing prices, leading to a reluctance among sellers to list their properties online. This regulatory environment allows real estate brokerages to sometimes post misleading prices to attract potential buyers, subsequently offering private information about other properties. In Singapore, the real estate market is heavily influenced by government-coordinated prices and evaluation companies' suggested prices. Conversely, in China, sellers have more freedom to set arbitrary listing prices. It is common practice for Chinese sellers to list their properties at higher prices, anticipating that buyers will negotiate and feel incentivized by securing a perceived better deal.

@@

Additionally, in the China's real estate market, brokerages still operate on a bilateral agency model, where sellers need to choose the agency that can help them sell their home in the fastest time and for the highest price possible for the transaction. However, due to the asymmetric information inherent in the real estate market, sellers face challenges in effectively informing and matching with potential buyers. In a perfectly competitive market, sellers would be indifferent in their choice of real estate agents. Nonetheless, as the market trends toward increased monopolization, sellers confront a dichotomous decision: engage a larger brokerage firm, which, despite higher fees, offers the potential for expedited transactions, or opt for a smaller brokerage with lower fees but potentially less efficient transaction facilitation.

While sellers might consider a co-listing strategy—listing their property with multiple brokerages—this approach is suboptimal for several reasons within China's real estate market. Despite previous literature, such as \citep{RePEc:kap:jrefec:v:67:y:2023:i:3:d:10.1007_s11146-021-09858-w}, indicating that the co-listing can be beneficial for clients under multiple-listing service. Specifically in China's real estate market, firstly, the exclusivity of contracts between sellers and agents often precludes the adoption of a co-listing strategy. Secondly, although sellers can list their properties with multiple brokerages, smaller agencies frequently lack a sufficiently broad client base, limiting their effectiveness in selling homes. Thirdly, engaging multiple brokers simultaneously can lead to reduced incentives among agents, as they perceive competition for the same property, diminishing their proactive efforts. Finally, while service cost variations between agencies are acknowledged, these costs are minor compared to the property's value and are more closely related to the risks associated with holding a financial asset. Consequently, risk-averse sellers are inclined to choose an agency that provides a guaranteed level of service.

@@

To evaluate the effects of platform-mediated consolidation, we consider the year Lianjia implemented its platform-based consolidation strategy as an exogenous shock to the market. This strategy primarily revolves around the ACN framework of Lianjia and the incorporation of various franchise stores into the network. Our empirical analysis indicates that this strategy significantly increases revenues and enhances the attraction of buyers and sellers, particularly in the number of house tours facilitated by the brokerage. However, our findings suggest that the platform-based consolidation does not effectively reduce the transaction period nor does it promote price concessions. This contrasts with the offline expansion strategy, which demonstrates a positive impact on promoting price concessions. While the economic impact of the online-based consolidation strategy is not as pronounced as that of the offline expansion strategy, it remains economically significant.

@@

The literature on the real estate market, particularly the role of real estate brokerages, is extensive and informative, starting with the foundational work of \citet{Rosen_hedonic} who introduced the hedonic pricing model. This model breaks down property prices by analyzing internal and external factors. However, it's worth noting that this model does not adequately account for market asymmetries and information disparities, leading to potential inaccuracies in pricing. A fundamental study by \citep{Akerlof_1970} highlights the significant impact of asymmetric information on market dynamics, using the market for used cars as an example. Here, the prevalence of low-quality goods, known as 'lemons', often leads to market inefficiencies, a problem that is mirrored in the real estate sector. The challenge of asymmetric information in real markets was further emphasized by \citet{grossman_impossibility_1980}, who questioned the feasibility of the effective market assumption, particularly under conditions of information disparity.

@@

Finally, the concept of the platform as a "two-sided market" or kind of intermediates that connects the buyer side and seller side digitally, \citep{10.1162/154247603322493212, Langley_Leyshon_2017}. Despite the significant attention given to online platforms, there is a lack of systematic analysis on the impact of offline stores of online platforms on market performance or on real estate brokerage. Therefore, this paper aims to fill this gap by examining the influence of offline stores associated with online platforms on the real estate market.

% With respect to the behavior of real estate brokerages, the research conducted by \citep{AGARWAL2019715} substantiates that these entities, acting as intermediaries in market transactions, possess superior knowledge of market dynamics. This informational superiority enables the intermediaries to use their bargaining power to secure discounts in the market. Similarly, \citet{HAN2015813} articulates that brokerages operating in unidirectional and bidirectional markets exhibit different levels of bargaining leverage, leading to different motivational drivers. This mechanism is in line with other research, which shows that properties with lower commission rates have a 5\% less likelihood of being sold and takes 12\% longer to sell \citep{10.1257/app.20160214}.

% Regarding the impact of online platforms on the real estate sector, research by \citep{ZUMPANO2003134} suggests that while the length of time buyers spend searching for properties remains unchanged, the scope of their search expands to include a greater number of online listings. \citet{ZHANG2021101104} show that the introduction of online platforms is associated with reductions in existing home prices and increased sales volumes, effects that are influenced by new home prices and household size. However, a comprehensive analysis of the influence of the physical stores of online platforms on the real estate market is still lacking in the literature.

% Finally, the impact of real estate intermediaries on the market can be decomposed into several aspects. Using a model based on the assumption of a perfectly competitive market in which an influx of brokers competitively enters the market, \citet{williams_agency_1998} shows that the presence of brokers in the market equilibrium exceeds the optimal number of allocations, thereby causing a reduction in social welfare. Moreover, the results show that neither brokers nor sellers are motivated to deviate from the equilibrium price structure, which coincides with the reservation price set by sellers. Complementary research in another study shows that a significant influx of brokers into the market is correlated with a decrease, rather than an increase, in house prices, along with a gradual decrease in transaction cycles within the market \citep{https://doi.org/10.1002/jae.2891}. Furthermore, the work of \citep{qu_identifying_2021-1} highlights the moderating role of broker commissions on the dissemination of market information during transactions. Their findings suggest that the use of a broker can significantly mitigate the concessions that sellers are forced to make in the transaction process, thereby enhancing their ability to complete a home sale more efficiently.

% Many literature has been conducted to study the real estate market, and the impact of real estate brokerages on the market, beginning with \citet{Rosen_hedonic}, which proposed a hedonic pricing model and decomposed the price by internal and external factors affecting it. However, the hedonic pricing model suffers from market asymmetry and information inequality. The seminal work on the impact of asymmetric information in markets is \citep{Akerlof_1970}, which demonstrated that markets for used cars tend to be dominated by low-quality goods, or 'lemons', leading to market inefficiencies. Furthermore, \citet{grossman_impossibility_1980} further argued that information effective market assumption is hard to hold in reality. Therefore, the real estate market, which is characterized by information asymmetry, is particularly vulnerable to the adverse selection problem. In this context, the role of real estate brokerages is crucial, as they act as intermediaries between buyers and sellers, providing valuable information and facilitating transactions.

% 由于房地产中介行业线上推广线下成交的机制，中介机构在线下门店中的服务性质对于其在客源方的影响具有很高的价值。链家通常选择在每个目标小区的周边开店便是该原理。链家通过在小区周边大范围开店，从而吸引卖方选择该机构进行挂牌，而又通过其广泛的平台客源来吸引市场中的买方从而获得更多的成交数量与成交收入。由于房地产中介行业线上推广线下成交的机制，中介机构在线下门店中的服务性质对于其在客源方的影响具有很高的价值。链家通常选择在每个目标小区的周边开店便是该原理。链家通过在小区周边大范围开店，从而吸引卖方选择该机构进行挂牌，而又通过其广泛的平台客源来吸引市场中的买方从而获得更多的成交数量与成交收入。

@@

This study focuses on the housing markets in ten major cities in China, namely Beijing, Shanghai, Chongqing, Tianjin, Shenzhen, Guangzhou, Chengdu, Hangzhou, Wuhan and Nanjing. These cities are not only pivotal to China's economic development, but also serve as exemplars of the broader trends and characteristics inherent in the China's real estate dynamics. Spanning from 2016 to 2022, the research period encapsulates a pivotal era in China's real estate sector. During the first phase of the study, from 2016 to 2019, the housing markets in these cities experienced a remarkable boom. This period was characterized by significant growth in property prices, supported by robust economic expansion and increased demand in these urban centers. However, the final phase of our study, from 2020 to 2022, paints a contrasting picture. During this period, China's overall economic growth rate has been slower significantly, which has also reflected in a slowdown in the real estate markets of these major cities. In addition, the Chinese government has implemented strict rules in Covid-19 protection, so the real estate agents in these major cities are significantly affected.

@@

The empirical findings indicate that in the first year of the consolidation strategy, Lianjia's transaction number did not show a statistically significant difference. However, after the first year, the transaction number demonstrated a significant positive increase, ranging from 2.9\% to 6.2\%. Additionally, the platform consolidation had a significantly positive impact on the number of house tours, with effects following the same trend as the transaction revenue. Furthermore, when comparing the effect of platform consolidation with the entry effect of offline stores, the result indicates that the effect is substantially more pronounced and more continuous. These results underscore the superior efficacy of platform consolidation in enhancing market performance and provide compelling evidence for the strategic advantage of consolidation over traditional offline expansion. However, in terms of the transaction period, the platformization strategy does not exhibit a significant effect, indicating that platformization does not assist brokerages in facilitating better matching and negotiation between sellers and buyers. Moreover, in terms of the platform's consolidation effect on price concessions, we find that the effect is significant after the first period, with a 4.2\% increase in the first year after the treatment and a 7.1\% increase in the second year. However, the effect becomes insignificant after the third year.

@@

To further investigate the impact of market concentration on the effectiveness of the platform consolidation strategy, we also classified the samples into low, moderate and high HHI groups and estimated the model separately for each group. The high HHI group, representing markets with higher concentration, revealed that the platform consolidation strategy does not confer significant benefits for Lianjia's operations. Conversely, in the low HHI group, indicative of less competitive markets, the platformization strategy significantly increases the transaction number. This suggests that the platform consolidation strategy is more effective in less competitive markets, enhancing Lianjia's competitiveness. In terms of the number of house tours, the effect of platform consolidation is consistent across both high and low HHI groups. This consistency aligns with the intuition that consumer preferences for different types of brokerages are similar, and individuals are equally likely to search for houses online regardless of the brokerage's market share. Moreover, our analysis in columns 5 to 8 shows that the platformization strategy does not have a significant effect on the transaction period or price concessions. This finding suggests that the platformization strategy does not facilitate better matching between buyers and sellers or improve the negotiation process. This aligns with the intuition that while the platformization strategy can attract more customers and generate revenue, it does not inherently improve the efficiency of matching buyers and sellers or negotiating terms because most of the transactions are still offline based.

@@

Our study highlights the transformative impact of Lianjia's strategic expansion in China's real estate brokerage industry through the implementation of the online-mediated consolidation strategy and the massive expansion of offline branches. Our empirical research demonstrates that Lianjia's approach, which seamlessly integrates online platforms with an extensive offline presence, significantly enhances revenue generation and influences consumer behavior through improved price concessions and increased number of house tours. Specifically, our results indicate that the expansion of Lianjia's stores leads to an increase in the company's market share in the region by 4.8\% to 9.1\% and attracts more clients, as evidenced by an increase in number of house tours by 2.3\% to 3.1\%. Additionally, the study reveals that while offline store expansion does not significantly affect the transaction period, but it facilitates better communication between buyers and sellers by contributing the price concession in transaction. Secondly, Lianjia's platform-mediated consolidation can also increase its transaction revenue by 2.9\% to 6.2\% and boost the number of house tours by 2.9\% to 3.0\%. However, this effect does not significantly impact communication, thus not affecting the price concession and transaction period. Lastly, we established the presence of localized network effects and found that Lianjia's network effects are primarily characterized by local clustering, with moderate network strength. The platform-mediated consolidation helps Lianjia achieve greater localized network effects, which in turn, enhances its long-term influence in the market.

@@

Future research could explore several potential directions. First, investigating the long-term impacts of online and offline integration on market competition and consumer behavior in various real estate markets globally could provide comparative insights. Second, examining the role of emerging technologies, such as artificial intelligence and blockchain, in further enhancing the efficiency and transparency of real estate transactions would be valuable. Third, assessing the socio-economic implications of platform-based monopolization, particularly in terms of access to affordable housing and regional economic disparities, could offer important policy implications. Lastly, exploring the adaptability of the online-offline integration model in other sectors, such as healthcare and education, could extend the applicability of these findings and contribute to a broader understanding of digital transformation across industries.

@@

\bibitem[Hui and Chan(2014)]{hui_foreign_2014}
Hui, E. C. M., and K. K. K. Chan. 2014. Foreign Direct Investment in China's Real Estate Market. \textit{Habitat International}, 43, 231-239.

@@

@@

@@

@@

\subsection{Alternative Methods} \label{subsec:alternative_methods}

>>>>

% Police brutality, law enforcement, and crime: Evidence from Chicago
\begin{abstract}
    \noindent This study examines the impact of offline store expansion by Lianjia, China's leading real estate brokerage, within the framework of platform-mediated consolidation. By analyzing micro-level transactions of second-hand houses from Lianjia in ten major Chinese cities from 2016 to 2022, this research investigates how the transaction patterns of traditional brokerages, characterized by the strategic clustering of offline stores, transition towards platform-mediated consolidation, thereby facilitating the development of an extensive franchise network. Utilizing a regression discontinuity design (RDD), the study quantifies the optimal influence radius of offline stores (410 meters) on housing transactions. Incorporating this optimal influence radius, the study further empirically estimates the effects of real estate brokerage's offline store expansion and platform-mediated consolidation on transaction properties. The results indicate that this strategy significantly boosts revenues and attracts more people to housing tours. The results also suggest that neither the platform-mediated strategy nor offline expansion affects the transaction period, but offline store expansion can indeed reduce the price gap between sellers and buyers. Additionally, we proposed a measure of the network effect and found that Lianjia's offline stores show a local clustering pattern with moderate network strength. We then analyzed the effect of platform-mediated consolidation on network strength and concluded that the effect is significantly positive. This study provides valuable insights into the synergy between offline store expansion and online platform development, elucidating future trajectories in the evolving real estate brokerage market and analogous sectors.
  \end{abstract}

@@

% https://www.zaobao.com.sg/realtime/china/story20231213-1455835#:~:text=%E6%8D%AE%E5%A4%AE%E8%A7%86%E6%96%B0%E9%97%BB%E6%8A%A5%E9%81%93%EF%BC%8C%E4%B8%AD%E5%9B%BD,%E6%96%B0%E5%BB%BA%E5%95%86%E5%93%81%E4%BD%8F%E5%AE%85%E4%BA%A4%E6%98%93%E9%87%8F%E3%80%82

According to the Ministry of Housing and Urban-Rural Development in China, the proportion of second-hand housing transactions rose to 37.1\% in 2023, with this trend showing continuous growth. Unlike the primary housing market, where transactions are straightforward, the secondary housing market necessitates sellers having access to buyers, thereby making transaction costs a critical factor for both parties. In this context, real estate brokers play a pivotal role in mitigating these costs. They provide essential market information, negotiation support, and legal assistance, thereby facilitating smoother and more efficient transactions in the real estate market. The involvement of brokers reduces the information asymmetry and transactional frictions that are characteristic of the secondary housing market, thus enhancing market efficiency. With the improvement of China's legal system in the real estate market, the brokerage market is expanding and becoming more prosperous. Especially in the context of China's burgeoning real estate market, brokerage firms are assuming an increasingly important role in facilitating the communications between buyers and sellers \citep{glaeser_real_2017}. Given the heterogeneous and "thin" nature of real estate goods \citep{HAN2015813}, the expertise and local market knowledge of real estate brokers have become indispensable in navigating the complex real estate landscape.

Chinese real estate listings market possesses distinct features characterized by the prominence of offline stores, setting it apart from the markets in other developed countries. Compared to the United States, where the Multiple Listing Service (MLS) provides comprehensive and reliable information online, facilitating transactions in a market where houses are typically situated far apart, the role of offline real estate stores is minimized. In contrast, Chinese real estate market is predominantly offline-based, with online listings serving mainly as references. Face-to-face interactions remain crucial for transactions. Additionally, the Chinese government imposes stringent restrictions on the online listing prices, leading to a reluctance among sellers to list their properties online. This regulatory environment allows real estate brokerages to sometimes post misleading prices to attract potential buyers, subsequently offering private information about other properties. In Singapore, the real estate market is heavily influenced by government-coordinated prices and evaluation companies' suggested prices. Conversely, in China, sellers have more freedom to set arbitrary listing prices. It is common practice for Chinese sellers to list their properties at higher prices, anticipating that buyers will negotiate and feel incentivized by securing a perceived better deal.

@@

Additionally, in the Chinese real estate market, brokerages still operate on a bilateral agency model, where sellers need to choose the agency that can help them sell their home in the fastest time and for the highest price possible for the transaction. However, due to the asymmetric information inherent in the real estate market, sellers face challenges in effectively informing and matching with potential buyers. In a perfectly competitive market, sellers would be indifferent in their choice of real estate agents. Nonetheless, as the market trends toward increased monopolization, sellers confront a dichotomous decision: engage a larger brokerage firm, which, despite higher fees, offers the potential for expedited transactions, or opt for a smaller brokerage with lower fees but potentially less efficient transaction facilitation.

While sellers might consider a co-listing strategy—listing their property with multiple brokerages—this approach is suboptimal for several reasons within Chinese real estate market. Despite previous literature, such as \citep{RePEc:kap:jrefec:v:67:y:2023:i:3:d:10.1007_s11146-021-09858-w}, indicating that the co-listing can be beneficial for clients under multiple-listing service. Specifically in Chinese real estate market, firstly, the exclusivity of contracts between sellers and agents often precludes the adoption of a co-listing strategy. Secondly, although sellers can list their properties with multiple brokerages, smaller agencies frequently lack a sufficiently broad client base, limiting their effectiveness in selling homes. Thirdly, engaging multiple brokers simultaneously can lead to reduced incentives among agents, as they perceive competition for the same property, diminishing their proactive efforts. Finally, while service cost variations between agencies are acknowledged, these costs are minor compared to the property's value and are more closely related to the risks associated with holding a financial asset. Consequently, risk-averse sellers are inclined to choose an agency that provides a guaranteed level of service.

@@

To evaluate the effects of platform-mediated consolidation, we consider the year Lianjia implemented its platform-mediated consolidation strategy as an exogenous shock to the market. This strategy primarily revolves around the ACN framework of Lianjia and the incorporation of various franchise stores into the network. Our empirical analysis indicates that this strategy significantly increases revenues and enhances the attraction of buyers and sellers, particularly in the number of house tours facilitated by the brokerage. However, our findings suggest that the platform-mediated consolidation does not effectively reduce the transaction period nor does it promote price concessions. This contrasts with the offline expansion strategy, which demonstrates a positive impact on promoting price concessions. While the economic impact of the online-based consolidation strategy is not as pronounced as that of the offline expansion strategy, it remains economically significant.

@@

The literature on the real estate market, particularly the role of real estate brokerages, is extensive and informative, starting with the foundational work of \citep{Rosen_hedonic} who introduced the hedonic pricing model. This model breaks down property prices by analyzing internal and external factors. However, it's worth noting that this model does not adequately account for market asymmetries and information disparities, leading to potential inaccuracies in pricing. A fundamental study by \citep{Akerlof_1970} highlights the significant impact of asymmetric information on market dynamics, using the market for used cars as an example. Here, the prevalence of low-quality goods, known as 'lemons', often leads to market inefficiencies, a problem that is mirrored in the real estate sector. The challenge of asymmetric information in real markets was further emphasized by \citet{grossman_impossibility_1980}, who questioned the feasibility of the effective market assumption, particularly under conditions of information disparity.

@@

Finally, the concept of the platform as a "two-sided market" or kind of intermediates that connects the buyer side and seller side digitally, \citep{10.1162/154247603322493212, Langley_Leyshon_2017, 10.1257/aer.100.4.1642}. \citet{https://doi.org/10.1111/j.1756-2171.2006.tb00036.x} characterizes real estate brokerages as a two-sided market. In this model, brokerages must effectively communicate and mediate between sellers and buyers, facilitating transactions and ensuring efficient market operations. Despite the significant attention given to online platforms and real estate broekerage's two-sided market \citep{10.1257/jep.23.3.125}, there is a lack of systematic analysis on the impact of offline stores of online platforms on market performance or on real estate brokerage. Therefore, this paper aims to fill this gap by examining the influence of offline stores associated with online platforms on the real estate market.

To our knowledge, this paper represents the pioneering empirical investigation into the effects of offline store expansion and platform-mediated consolidation within the real estate brokerage market. Furthermore, it is the first to analyze the local network effects within the specific context of real estate transactions. Additionally, this paper systematically examines how informational advantages can enhance brokerage revenue within the framework of local network effects. By delving into these dynamics, we aim to contribute to the broader economics literature by providing a nuanced understanding of how offline and online integration influences market behavior and outcomes. Our findings offer meaningful insights into the strategic decisions of real estate brokerages, highlighting the significance of network effects and informational advantages in shaping competitive advantage and market performance. This research not only fills critical gaps in the literature but also provides a comprehensive framework for future studies to explore the intersection of offline expansion, digital consolidation, and local network effects in various economic contexts. By systematically examining these phenomena, we enhance the understanding of how technological and infrastructural developments can drive revenue generation and market consolidation in the real estate industry and beyond.

@@

This study focuses on the housing markets in ten major cities in China, namely Beijing, Shanghai, Chongqing, Tianjin, Shenzhen, Guangzhou, Chengdu, Hangzhou, Wuhan and Nanjing. These cities are not only pivotal to China's economic development, but also serve as exemplars of the broader trends and characteristics inherent in the Chinese real estate dynamics. Spanning from 2016 to 2022, the research period encapsulates a pivotal era in Chinese real estate sector. During the first phase of the study, from 2016 to 2019, the housing markets in these cities experienced a remarkable boom. This period was characterized by significant growth in property prices, supported by robust economic expansion and increased demand in these urban centers. However, the final phase of our study, from 2020 to 2022, paints a contrasting picture. During this period, China's overall economic growth rate has been slower significantly, which has also reflected in a slowdown in the real estate markets of these major cities. In addition, the Chinese government has implemented strict rules in Covid-19 protection, so the real estate agents in these major cities are significantly affected.

@@

The empirical findings indicate that in the first year of the consolidation strategy, Lianjia's transaction number did not show a statistically significant difference. However, after the first year, the transaction number demonstrated a significant positive increase, ranging from 2.9\% to 6.2\%. Additionally, the platform consolidation had a significantly positive impact on the number of house tours, with effects following the same trend as the transaction revenue. Furthermore, when comparing the effect of platform consolidation with the entry effect of offline stores, the result indicates that the effect is substantially more pronounced and more continuous. These results underscore the superior efficacy of platform consolidation in enhancing market performance and provide compelling evidence for the strategic advantage of consolidation over traditional offline expansion. However, in terms of the transaction period, the consolidation strategy does not exhibit a significant effect, indicating that consolidation does not assist brokerages in facilitating better matching and negotiation between sellers and buyers. Moreover, in terms of the platform's consolidation effect on price concessions, we find that the effect is significant after the first period, with a 4.2\% increase in the first year after the treatment and a 7.1\% increase in the second year. However, the effect becomes insignificant after the third year.

@@

To further investigate the impact of market concentration on the effectiveness of the platform consolidation strategy, we also classified the samples into low, moderate and high HHI groups and estimated the model separately for each group. The high HHI group, representing markets with higher concentration, revealed that the platform consolidation strategy does not confer significant benefits for Lianjia's operations. Conversely, in the low HHI group, indicative of less competitive markets, the consolidation strategy significantly increases the transaction number. This suggests that the platform consolidation strategy is more effective in less competitive markets, enhancing Lianjia's competitiveness. In terms of the number of house tours, the effect of platform consolidation is consistent across both high and low HHI groups. This consistency aligns with the intuition that consumer preferences for different types of brokerages are similar, and individuals are equally likely to search for houses online regardless of the brokerage's market share. Moreover, our analysis in columns 5 to 8 shows that the consolidation strategy does not have a significant effect on the transaction period or price concessions. This finding suggests that the consolidation strategy does not facilitate better matching between buyers and sellers or improve the negotiation process. This aligns with the intuition that while the consolidation strategy can attract more customers and generate revenue, it does not inherently improve the efficiency of matching buyers and sellers or negotiating terms because most of the transactions are still offline based.

@@

Our study highlights the transformative impact of Lianjia's strategic expansion in Chinese real estate brokerage industry through the implementation of the online-mediated consolidation strategy and the massive expansion of offline branches. Our empirical research demonstrates that Lianjia's approach, which seamlessly integrates online platforms with an extensive offline presence, significantly enhances revenue generation and influences consumer behavior through improved price concessions and increased number of house tours. Specifically, our results indicate that the expansion of Lianjia's stores leads to an increase in the company's market share in the region by 4.8\% to 9.1\% and attracts more clients, as evidenced by an increase in number of house tours by 2.3\% to 3.1\%. Additionally, the study reveals that while offline store expansion does not significantly affect the transaction period, but it facilitates better communication between buyers and sellers by contributing the price concession in transaction. Secondly, Lianjia's platform-mediated consolidation can also increase its transaction revenue by 2.9\% to 6.2\% and boost the number of house tours by 2.9\% to 3.0\%. However, this effect does not significantly impact communication, thus not affecting the price concession and transaction period. Lastly, we established the presence of localized network effects and found that Lianjia's network effects are primarily characterized by local clustering, with moderate network strength. The platform-mediated consolidation helps Lianjia achieve greater localized network effects, which in turn, enhances its long-term influence in the market.

@@

Future research could explore several potential directions. First, investigating the long-term impacts of online and offline integration on market competition and consumer behavior in various real estate markets globally could provide comparative insights. Second, examining the role of emerging technologies, such as artificial intelligence and blockchain, in further enhancing the efficiency and transparency of real estate transactions would be valuable. Third, assessing the socio-economic implications of platform monopolization, particularly in terms of access to affordable housing and regional economic disparities, could offer important policy implications. Lastly, exploring the adaptability of the online-offline integration model in other sectors, such as healthcare and education, could extend the applicability of these findings and contribute to a broader understanding of digital transformation across industries.

@@

\bibitem[Hui and Chan(2014)]{hui_foreign_2014}
Hui, E. C. M., and K. K. K. Chan. 2014. Foreign Direct Investment in Chinese real estate Market. \textit{Habitat International}, 43, 231-239.

@@

\bibitem[Rochet and Tirole(2006)]{https://doi.org/10.1111/j.1756-2171.2006.tb00036.x}
Rochet, J.-C., and J. Tirole. 2006. Two-Sided Markets: A Progress Report. \textit{The RAND Journal of Economics} 37(3): 645-667. % https://doi.org/10.1111/j.1756-2171.2006.tb00036.x.

@@

\bibitem[Rysman(2009)]{10.1257/jep.23.3.125}
Rysman, M. 2009. The Economics of Two-Sided Markets. \textit{Journal of Economic Perspectives} 23(3): 125-143. % https://doi.org/10.1257/jep.23.3.125.

@@

\bibitem[Weyl(2010)]{10.1257/aer.100.4.1642}
Weyl, E. G. 2010. A Price Theory of Multi-Sided Platforms. \textit{American Economic Review} 100(4): 1642-1672. % https://doi.org/10.1257/aer.100.4.1642.

@@
